What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-01-02 paper/main.tex
cleaned up section 6

The soundness of each of these translations can be proven by reasoning about the  semantics detailed in \cref{def:omega-semantics}. A full proof is not provided at this time.

@@

KYR: Here we nicely show (with pictures as much as possible) all of the individual statistics and results we gathered (note aggregation occurs below).
\paragraph{Real-world datasets} We study the feasibility of our tool on a benchmark suite of LTL formulas gathered from real world use cases.

@@

\paragraph{Denouement}
KYR: aggregate and summarize all experiments here.

<image>
caption: For all of the <large number> of real LTL formulas historically used to analyze real systems, \tool efficiently yields usable, readable timeline visualizations.

>>>>

The soundness of each of these translations can be proven by reasoning about the  semantics detailed in \cref{def:omega-semantics}. A full proof is not provided here.

@@

%KYR: Here we nicely show (with pictures as much as possible) all of the individual statistics and results we gathered (note aggregation occurs below).
\paragraph{Real-world datasets} We study the feasibility of our tool on a benchmark suite of LTL formulas gathered from real world use cases.

@@

%\paragraph{Denouement}
%KYR: aggregate and summarize all experiments here.

%<image>
%caption: For all of the <large number> of real LTL formulas historically used to analyze real systems, \tool efficiently yields usable, readable timeline visualizations.
